### 2019-06-17 dantzig_selector/report/1_introduction.tex
Proof: Concentration ineq.: Progress of
Introduction: Add OMP description

\Result
{Algorithm: Dantzig Selector}
{
\startitemize[n]
\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
\item Calculate
\Disp {
\NC \V {h}
\LA \NC \startcases
\NC \Min {\V {h}'} \Q \MC \VNm {\V {h}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
\stopcases \NR
}
\item Output \m {\V {h}}.
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item \color[red]{(To be done)}
\stopitemize
}
From Tropp and Gilbert (2007a), OMP recovers \m {x} completely, with overwhelming probability.

It is interesting to note that, ever since, scholars has applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.

@@

With (), scholars often exploit the relation

\Result
{Lemma.}
{
Suppose \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}, \M{X} \in \MB {M}_{\MB {K}} \SB {N_2, N_3}, \M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}},
Then
\Disp {
\NC \mathrm{vec} \RB {\M{A}\M{X}\M{B}}
= \NC \RB {\M{B}^\Tr \otimes \M{A}} \mathrm{vec} \SB {\M{X}} \NR
}
}

>>>>

\Result
{Algorithm: Dantzig Selector}
{
\startitemize[n]
\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
\item Calculate
\Disp {
\NC \Hat {\V {h}}
\LA \NC \startcases
\NC \Min {\V {h}'} \Q \MC \VNm {\V {h}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
\stopcases \NR
}
\item Output \m {\Hat {\V {h}}}.
}

@@

\Result
{Algorithm: Orthogonal Matching Pursuit}
{
\startitemize[n]
\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
\item Initialize
\Disp{
\NC \V{r}
\LA \NC \V{y} \NR[+]
\NC S
\LA \NC \varnothing \NR[+]
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
\Disp{
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm{argmax}}
\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR[+]
}
and insert \m {S \LA S \cup {i}}.
\item Compute
\Disp{
\NC \M{\Phi} ^\ddagger
\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \NR[+]
\NC \V{r}
\LA \NC \V{y} -\M{\Phi} ^\ddagger \V{y} \NR[+]
}
\item Break if
\Disp{
\NC \VNm {\M{\Phi} ^\ddagger} _1
<\NC 1 \NR[+]
}
where \m {\VNm {\M{\Phi} ^\ddagger} _1} denotes the operator norm.
\item Output 
\Disp {
\NC \Hat {\V {g}}
\LA \NC \M{\Phi} ^\ddagger \V{y} \NR[+]
}
\stopitemize
}
Here \m {\V{r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).

From Tropp and Gilbert (2007a), the probability OMP recovers \m {h} completely is overwhelming.

It is interesting to note that, ever since, the channel sensing scholars have applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.

@@

With (), scholars often exploit the relation
\Result
{Lemma.}
{
Suppose \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}, \M{X} \in \MB {M}_{\MB {K}} \SB {N_2, N_3}, \M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}},
Then
\Disp {
\NC \Rm{vec} \SB {\M{A}\M{X}\M{B}}
= \NC \RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB {\M{X}} \NR
}
}
